### 2019-03-27 tii/tex/intro.tex
Fix typo proposed by reviewer2.

To make things worse, we note that the above deficiencies generally exist in most of the DAG computing frameworks. 
As a result, even we can effectively resolve the above deficiencies by modifying one framework, updating one application at a time is impractical given the sheer number of computing frameworks available today.

>>>>

We note that the above deficiencies generally exist in most of the DAG computing frameworks. 
As a result, even though we can effectively resolve the above deficiencies by modifying one framework, updating one application at a time is impractical given the sheer number of computing frameworks available today.

### 2019-03-27 tii/tex/optimization.tex
Fix typo proposed by reviewer2.

\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/hash_pre}
		\caption{Linear Regression Prediction of Hash Partitioner\newline}
		\label{fig:hash_pre}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/range_pre_sample}
		\caption{Linear Regression and Sampling Prediction of Range Partitioner2222}
		\label{fig:range_pre_sample}
		\vspace{1em}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
		\caption{Prediction Relative Error of Range Partitioner\newline}
		\label{fig:prediction_relative_error}
	\end{subfigure}
	\caption{Reduction Distribution Prediction}
	\label{fig:dis}
	\vspace{-1em}
\end{figure*}

@@

\noindent
\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Heuristic MinHeap Scheduling for Single Shuffle}
\label{hminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{schedule}{$m, host\_ids, p\_reduces$}
		\State $m\gets$ partition number of map tasks
		\State $R\gets$ sort $p\_reduces$ by size in non-increasing order
		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
		\State $idx\gets 0$
		\While{$idx <$ len$R$}
		% \Comment{Schedule reduces by MinHeap}
		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
		\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
		\State Sift down $M\left[0\right]$ by $size$
		\State $idx\gets idx-1$
		\EndWhile
		\State $max\gets$ maximum size in $M$
		% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
		\ForAll{$reduce$ in $R$}
		\Comment{Heuristic locality swap}
			\If{$reduce.assigned\_id \neq reduce.host\_id$}
				\State $p\gets reduce.prob$
				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
				\State $upper\_bound \gets \left(1 + norm\right) \times max$
				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
			\EndIf
		\EndFor
		\Return $M$
	\EndProcedure
	\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
		\State Swap tasks between node $host\_id$ and node $assigned\_id$
		\State of $reduce$ without exceeding the $upper\_bound$
		\State of both nodes.
		\State Return if it is impossible.
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}

@@

\subsubsection{Cope with Multiple Shuffle Dependencies}
% \ifrevision
% \marginpar{E5}
% \fi
A reduce stage can have more than one shuffle dependencies in the current DAG computing frameworks. 
The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
For those pending shuffles, it is impossible to predict their sizes. 
This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
But doing this introduces large overhead such as extra task serialization. 
To avoid violating the optimization from framework, we present the Accumulated Heuristic Scheduling algorithm to cope with multiple shuffle dependencies.

>>>>

\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/hash_pre}
		\caption{Linear Regression Prediction of Hash Partitioner\newline}
		\label{fig:hash_pre}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/range_pre_sample}
		\caption{Linear Regression and Sampling Prediction of Range Partitioner}
		\label{fig:range_pre_sample}
		\vspace{1em}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
		\caption{Prediction Relative Error of Range Partitioner\newline}
		\label{fig:prediction_relative_error}
	\end{subfigure}
	\caption{Reduction Distribution Prediction}
	\label{fig:dis}
	\vspace{-1em}
\end{figure*}

@@

\noindent
\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Heuristic MinHeap Scheduling for Single Shuffle}
\label{hminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{schedule}{$m, host\_ids, p\_reduces$}
		\State $m\gets$ partition number of map tasks
		\State $R\gets$ sort $p\_reduces$ by size in non-increasing order
		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
		\State $idx\gets 0$
		\While{$idx <$ len$R$}
		% \Comment{Schedule reduces by MinHeap}
		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
		\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
		\State Sift down $M\left[0\right]$ by $size$
		\State $idx\gets idx+1$
		\EndWhile
		\State $max\gets$ maximum size in $M$
		% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
		\ForAll{$reduce$ in $R$}
		\Comment{Heuristic locality swap}
			\If{$reduce.assigned\_id \neq reduce.host\_id$}
				\State $p\gets reduce.prob$
				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
				\State $upper\_bound \gets \left(1 + norm\right) \times max$
				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
			\EndIf
		\EndFor
		\Return $M$
	\EndProcedure
	\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
		\State Swap tasks between node $host\_id$ and node $assigned\_id$
		\State of $reduce$ without exceeding the $upper\_bound$
		\State of both nodes.
		\State Return if it is impossible.
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}

@@

\subsubsection{Cope with Multiple Shuffle Dependencies}
% \ifrevision
% \marginpar{E5}
% \fi
A reduce stage can have more than one shuffle dependency in the current DAG computing frameworks. 
The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
For those pending shuffles, it is impossible to predict their sizes. 
This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
But doing this introduces large overhead such as extra task serialization. 
To avoid violating the optimization from framework, we present the Accumulated Heuristic Scheduling algorithm to cope with multiple shuffle dependencies.
